---
format:
  html:
    page-layout: custom
execute:
  echo: false
  warning: false
  messages: false
---

```{r setup}
library(dplyr)
library(tidyr)
library(stringr)
library(readxl)
library(reactable)

source("logic/fondo_table.R", echo = FALSE, verbose = FALSE)
```

<style>
@media only screen and (max-width: 800px) {
  body {
    font-size: 14px;
    padding: 5px;
  }
  h2{
  margin-top: 20px;
  font-size: 16px;
}
}

h2{
 border-bottom: none;
}

.aportes-table {
  margin-top: 1rem;
  border: none;
  border-radius: 4px;
  box-shadow: 0 4px 8px 0 rgba(0, 0, 0, 0.1);
  height: 70vh;
}

.header {
  background-color: hsl(213, 45%, 97%);
  border-bottom-color: hsl(213, 33%, 93%);
  border-bottom-width: 1px;
  border-top: 1px solid hsl(213, 33%, 93%);
  color: hsl(213, 13%, 33%);
}

.rt-tbody{
border: 1px solid hsl(213, 33%, 93%);
}

.header[aria-sort]:hover,
.header[aria-sort]:focus {
  color: hsl(213, 55%, 50%);
}

</style>


## Tabla de aportes al `r format(max(aportes$fecha), "%d de %B del %Y", locale = "spanish")` {.px-md-5 .d-flex .flex-column .align-items-center}

::: {d-flex}
<span class="badge bg-success">Ingreso `r format(sum(aportes$aporte), big.mark = ",")`</span> {{< fa minus >}}
<span class="badge bg-danger">Gasto `r format(sum(gastos$monto), big.mark = ",")`</span> {{< fa equals >}}
<span class="badge bg-primary">Balance `r format(sum(aportes$aporte) - sum(gastos$monto), big.mark = ",")`</span>
:::

::: { .panel-tabset }

### Ingresos
```{r}
tabla_aportes
```

### `r stringr::str_to_sentence(format(max(aportes$fecha), "%B"))`
```{r}
tabla_current_month
```

### `r stringr::str_to_sentence(format(max(aportes$fecha) - months(1), "%B"))`
```{r}
tabla_current_month
```



### Gastos

```{r}
tabla_gastos
```


### Multas

```{r}
tabla_multas
```

:::